\chapter{Requirements}

This chapter seeks to outline the fundamental requirements that drive the development of the product, both in terms of functional and non-functional requirements, all prioritized using MoSCoW-style prioritization. Requirements are written in a \textit{"Users must/should/could/would be able to x"} format.

Below are the initial requirements decided on during the projects infancy. In the context of a commercially developed product for a particular client, they represent what perhaps would be received from the client when they first commission the system, for then to be further analyzed in the next chapter.

\begin{itemize}

    \item \textit{Multiple users must be able to connect to the same room.}
    \item \textit{Users should be able to connect to each other with audio and video streams.}
    \item \textit{Users should be able to connect to each other with audio and video streams.}
    \item \textit{User should be able to hear other users audio streams.}
    \item \textit{Users must be able to create different rooms.}
    \item \textit{User must be able to connect to a room using an ID.}
    \item \textit{Room owners could be able to delete created rooms.}
    \item \textit{User should be able to move around the room.}
    \item \textit{Users should be able to send text messages the room.}
    \item \textit{The sound from other users could reflect the distance between each other.}
    \item \textit{The user would be able to login/register a permanent account.}
    \item \textit{Room owners would be able to mute certain users.}
    \item \textit{Room owners would be able to send priority text messages.}
    \item \textit{A browser-based session client must be available to users.}
    \item \textit{The back end could support any type of user client through a public API.}
    \item \textit{The back end HTTP servers must be encrypted through HTTPS to protect end-user data for security.}
    \item \textit{The system must be able to scale horizontally.}
    \item \textit{The system should be able to be deployed using containerization technologies.}
    
\end{itemize}


\section{Conclusion}

This chapter outlines a list of initial requirements as if received by a client commissioning the system, including requirements related to creating and joining rooms, as well as allowing users to stream proximity-based audio and video to each other. Furthermore, there are a number of requirements revolving around the qualities of the system, such as a security and scalability.