\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}
\textbf{\authors} \newline

We would like to thank ourselves for making it through this project despite the ever-encompassing dread of the quarantine along with the number of technical difficulties encountered throughout the project.

We would also like to thank the creator of this thesis template, because they asked to by leaving a line which these particular lines are based directly upon, and because the template has allowed us to focus on the important aspects of writing this report, rather than wasting time setting everything up.

But most of all, we would like to thank our supervisors:

\textbf{Leon Bonde Larson}, M.Sc. Robotics, The Maersk Mc-Kinney Moller Institute \newline
We extend our gratitude to Leon for his significant help in getting us through this project with a satisfactory result. His steady, firm-but-fair, and thoroughly detailed feedback has been a persistent inspiration for improvements, and both team members feel that we have learned magnitudes from it. Even if the final exam goes poorly for whatever reason, the team believes that it will all have been easily worth it due to the many skills we have learned and improved.

\textbf{Mathias Neerup}, Mærsk Mc-Kinney Møller Instituttet \newline
We extend our gratitude to Mathias for providing excellent technical support helping with the design and implementation of the system. He has gone above-and-beyond in providing the information we needed, when we needed it, and we feel confident that the final product would not have reached the same height without his help.

