\chapter{Reading Instructions}

This report is written in an effort to explain and document the development of a CoffeeBreak solution, documenting every step of the way from inception to conclusion. Each individual chapter focuses on a particular aspect of the project as a whole, and seeks to be mostly understandable without having a full understanding of the project as a whole. Each chapter additional begins with a short introduction about the chapter in order to provide some context on what that chapter is about, and the project subdomain it encompasses. Some chapters include a conclusion of the chapter at the very end if applicable, which serves as a synopsis of the chapter as a whole, with the goal being that the reader is able to understand the most essential aspects of the chapter though the introduction and conclusion alone, however the reader is unlikely to achieve full understanding of the project by merely skimming these parts. The report is written as the final part of the project.

The report is written with the primary target audience being on an academical level similar to three years of formal education within the field of software engineering at least. The goal is for anyone with such qualifications to be able to follow and understand the majority of the report without much difficulty. The secondary target audience is anyone with familiarity with software development in general, who should be able to understand most of the report, aside from perhaps the most technical aspects. Finally, the tertiary target audience is the general public who should be able to understand the essentials of the report.

The primary goal of this project has been to develop a robust and fully featured CoffeeBreak solution, which will the focus of the majority of this report. Additionally, the secondary goal of comparing different solutions in terms of complexity and performance is the focus of some particular chapters, primarily the Abstract and Result chapters, as well as some parts of the Methodology and Process chapter.

Naturally, ambitious projects rarely live up to their original goals, in particular as the development of this project took place during the \emph{hopefully as of writing} latter half of Covid-19 pandemic, and by extension difficulties with what is colloquially known as \textit{Quarantine Depression}. Individual and team reflections discussing this and more, as well as individual and team learning from the project will be discussed towards the end of this report in the Evaluation and Reflections chapter.

Technologies, methodologies, facts, and products referenced in this report will be supported by the IEEE standard citation, wherein any of the aforementioned elements will be followed by a [x] notation, which links to a corresponding entry in the Bibliography chapter.

Occasionally, the reader may come across footnotes denoted by an $^x$ superscript notation, and a corresponding footnote at the buttom of the page.\footnote{Like this.} These footnotes usually contain information which may provide further context or some other information that might be of interest to the reader.